## Case Study

Here, we present a case study for augmented inverse probability weigthed estimator using the simulated data in the paper.

To get the package ready, here are the few steps needed.
```{r,eval=FALSE}
# Clean up the workspace:
rm(list = ls())
# Install required the packages: 
install.packages('DynTxRegime')
install.packages('rgenoud')
# Load the packages:
library(DynTxRegime)
library(rgenoud)
```
The 'rgenound' package is required for maximizing AIPWE. 


<!-- create the one-stage BMIdata by deleting month12BMI and A2 -->
```{r, echo=FALSE, message=FALSE}
# Clean up the workspace:
rm(list = ls())
# Load the packages:
library(DynTxRegime)
library(rgenoud)
# hide month12BMI and A2 and create the single stage bmiDataOne
data(bmiData)
bmiDataOne <- bmiData[ ,c(-6,-8)]
bmiDataOne$A1[which (bmiDataOne$A1=="MR")] <- 1L
bmiDataOne$A1[which (bmiDataOne$A1=="CD")] <- 0L
bmiDataOne$A1 <- as.integer(bmiDataOne$A1)
bmiDataOne$y <- -100*(bmiDataOne[,5] - bmiDataOne[,4])/bmiDataOne[,4]
```

We use the same dataset used in outcome regression method, [bmiDataOne](potentially put the server link to it, "Previous on bmiDataOne"). Dataset has been prepared by the same steps as in outcome regression method case study.
```{r}
# Data
head(bmiDataOne)
```

AIPWE is wrapped in the function 'optimalSeq' in the 'DynTxRegime' package. First, we need to tell 'optimalSeq' which columns of data correspond to treatments. To do so, we assign treatment column name ``A1" to tx.vars.
```{r}
# tx.var tells optimal which columns of data correspond to treatments.
tx.vars <- "A1"
```
Second step is to build modeling object for the [propensity scores](possible link, "A propensity score is the probability of assigning a subject to a specific treatment given his/er observed covariates. More details on IPWE.") of treatments. As before, we use the "buildModelObj" function to create this modeling object.
```{r}
# modeling.object for propensity of treatment.
moPropen <- buildModelObj(model = ~  gender + race + parentBMI + baselineBMI + month4BMI, solver.method = 'glm', solver.args = list( 'family' = 'binomial' ),  predict.method = 'predict.glm', predict.args = list( 'type' = 'response'))
```
The covariates included in moPropen modeling object are gender, race, parentBMI and baselineBMI. solver.method is used to specify the method for fitting models, and Generalized Linear Model ('glm') is used here. The "solver.args"" is a list of additional arguments needed for the specific "solver.method". By defining 'family' as 'binomial' in the list, the 'logit' link is used for 'glm' fitting . The "predict.method" is to define the R function for predictions, and 'predict.glm' is used here. If not specified, R generic prediction function 'predict' is used. the type of prediction required. The "predict.args" is a list of additional arguments for "predict.method". In the list, by setting 'type' to 'response', prediction is made on the scale of the response variable. For more details, use commands "help(buildModelObject)" and "help(glm)"
 
The next step is to build a modeling object for the conditional expectation model.
```{r}
# modeling.object for conditional expectation models
expec.main <- buildModelObj(model =  ~ parentBMI + baselineBMI + A1 + A1:(parentBMI + baselineBMI),  solver.method =  'lm' )
expec.cont <- NULL 
```
For simplicity, the conditional expectation is modeled as a whole, without seperately modeling moMain and moCont as in outcome regressiom method.  The model includes the covariates, parentBMI , baselineBMI , A1 and the interaction term A1*(parentBMI + baselineBMI). It is also an option to model the main effect and the contrast seperately as in outcome regression method. More details for building modeling objects, please see the case study of [outcome regression method](possible link, "Case study of outcome regression method") . If we set both expec.main and expec.cont to be NULL, then [Inverse Probability Weighted Estimator](possible link, "more details on IPWE") is used here.


Then, the next step is to define the class of treatment regim rules of interest. 
```{r}
# treatment regime rules at the decision point.
tx.rules <- function(a,b,c,data){
  as.numeric(a + b*bmiDataOne$baselineBMI + c*bmiDataOne$parentBMI > 0 )} 
```
Here any regimes in the class of linear combination of baselineBMI and parentBMI plus a constant is of interest, that is $\mathbb{1}\{ a + b \times X_{baselineBMI} + c \times X_{parentBMI}  >0\}$. Therefore, only the sign of the regime matters for treatment assignment. We can normalize the vector $(a, b, c)$ later for achieving an unique solution.  Finding the optimal regime is equivalent to find a, b and c, by maximizing AIWPE.

We use function 'genound' to maximize AIWPE. To do so, we need provide the bounds for ( a, b , c) and a starting point.
```{r}
# genoud requires bounds for each parameter
c1 <- c(-1,-1,-1)
c2 <- c( 1, 1, 1)
Domains <- cbind(c1,c2)
starts <- c(0,0,0)
```
The starting point is set to be (0,0,0). The search region for (a, b, c) is a cuboid bounded by (-1, -1, -1) and (1, 1, 1).

Another parameter needed for [genoud](https://cran.r-project.org/web/packages/rgenoud/rgenoud.pdf, "Genetic algorithm for optimization: rgenoud ") is population size for genetic algorithm, "pop.size". A large value for "pop.size" is suggested. Here for saving runtime of this example, we set it to 50.
```{r}
# recommond large value, such as 1000, for pop.size.
pop.size <- 50
```
Then, we now can call the "optimalSeq" function and use AIPWE to estimate an optimal regime within the class of regime defined above.
```{r, message=FALSE, results='hide'}
ft <- optimalSeq(moPropen = moPropen,
                 moMain = expec.main,
                 moCont = expec.cont,
                 data = bmiDataOne,
                 response = bmiDataOne$y,
                 txName = tx.vars,
                 regimes = tx.rules,
                 pop.size = pop.size,
                 starting.values = starts,
                 Domains = Domains)
```
We can then use the "regimeCoef" function to retrieve the estimated coefficients, $(\widehat{a}, \widehat{b}, \widehat{c})$ of the optimal regime. As only the direction of the regime matters for treatment assignment, we normalize the coefficent vector.
```{r, eval=F}
# The  normalized estimated optimal treatment regime
est <- regimeCoef(ft)
est <- est/sqrt(est %*% est)
```

The estimated mean potential outcome for the treatment regime can be retrived by the function "estimator".
```{r, eval=F}
# defined by the regime
estimator(ft)
```

To access value objects of regression steps, we can use the "outcome" and the "propen" function.
```{r, eval=F}
outcome(ft)
propen(ft)
```

To access the information of the optimization step, we can use the "genetic" function.
```{r, eval=F}
genetic(ft) 
```

To retrieve optimal treatment for training data, we can use the "opt" function.
```{r, eval=F}
optTx(ft)
```
Finally, the "summary" function summarize the estimated optimal regime.
```{r}
summary(ft)
```




